\documentclass[a5paper,12pt]{book}
\usepackage{geometry}
\geometry{a5paper}
\raggedright
\title{Vajra-Prajna-Parami}
\author{Translated by Gasin An}
\date{}
\begin{document}

    \maketitle

    \pagestyle{empty}
    ~\newpage
    \pagestyle{headings}

    \setcounter{page}{1}

    ~

    \marginpar{\raggedright I} I heard that: One day, the Buddha was in Jetavanavihara, Sravasti with one thousand two hundred and fifty great bhiksus. Just the time for meal, the Buddha wore his clothes, took his bowl, and entered Sravasti City. He begged for food from door to door, then returned. After the meal, he put away his clothes and bowl, washed his feet, then placed his cushion and sat down.

    ~

    \marginpar{\raggedright II} At that time, elder Subhuti was in the multitude. He stood up from his seat with his right shoulder exposed, then went to the front of the Buddha, got down on his right knee, and held his palms together respectfully. He said, ``Rare, you, the Respected! You, the Like-Arrived, are wise in protecting and educating all bodhisattvas. The Respected! If kind people spring up the Anuttara-Samyak-Sambodhi will, how can they keep their will, and subdue their unwise minds?'' The Buddha answered, ``That's good! That's good! As you said, I am wise in protecting and educating all bodhisattvas. You are now listen carefully, thus I ought to tell you: The kind people, who spring up the Anuttara-Samyak-Sambodhi will, need to keep their will, and subdue their unwise minds in a certain way.'' ``Yes! The Respected, we are glad to listen for that.''

    ~

    \marginpar{\raggedright III} The Buddha said, ``All bodhisattvas, or mahasattvas, need to subdue their unwise minds in this way: I would like to make all kinds of lives achieve Nothing-Remained-Nirvana and save them, no matter how they appeared, no matter whether they can be objects of sensations, no matter whether they have thoughts, even if they not only have thoughts but also have no thoughts, however, if I have saved infinite lives, actually no `lives' will have been saved. Why? Subhuti! If `bodhisattvas' have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}, they can't be bodhisattvas.''

    ~

    \marginpar{\raggedleft IV} And then the Buddha said, ``Subhuti! All bodhisattvas should make Alms-Giving, but they mustn't be obsessed with anything, which means, they mustn't be obsessed with what are seen, heard, smelled, tasted, touched, and they mustn't be obsessed with consciousness. Subhuti! All bodhisattvas should make Alms-Giving, but they mustn't be obsessed with Phenomena. Why? If bodhisattvas are just like what I said, the rewards from their merits, will not be able to thought about. Subhuti! What is your opinion? Can the east vacuum be thought about?'' ``No! It can't, the Respected.'' ``Subhuti! Can the south vacuum, the west vacuum, or the north vacuum, be thought about? Can the vacuum below or the vacuum above be thought about?'' ``No! They can't, the Respected.'' ``Subhuti! If bodhisattvas are just like what I said, the rewards from their merits, will also not be able to thought about. Subhuti! All bodhisattvas, must subdue their unwise minds in the way I told!''

    ~

    \marginpar{\raggedright V} ``Subhuti! What is your opinion? Can anyone recognize the Like-Arrived by the `body'?'' ``No, the Respected! No one can recognize the Like-Arrived by the `body'. Why? You said `body', but it is not body.'' The Buddha told Subhuti, ``All Phenomena, are illusions. If someone knows that none of Phenomena is `Phenomenon', the Like-Arrived will be comprehended.''

    ~

    \marginpar{\raggedright VI} Subhuti asked the Buddha, ``The Respected! After your Nothing-Remained-Nirvana for two thousand years, when the Doctrine-Decayed-Era may come, will any life produce genuine belief after knowing these words?'' The Buddha answered Subhuti, ``Don't say that! At that time, there will be some lives, who keep Precept-Observing then reap rewards, being able to have belief that these words are truth after knowing them. You should realize that these lives have followed infinite buddhas, and cultivated all good causes. Subhuti! Who produce the single pure belief after knowing these words, will have reaped such infinite rewards: This is clearly realized by me. Why? These lives no longer have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. What's more, these lives no longer have not only Wisdom-Concept but also Anti-Wisdom-Concept. Why? If these lives are obsessed with Phenomena, they will have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. If they have Wisdom-Concept, they will have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. If they have Anti-Wisdom-Concept, however, they will also have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. Therefore, we shouldn't have not only Wisdom-Concept but also Anti-Wisdom-Concept. Thus I often say, `You bhiksus, know that I compare Wisdom to boat.' Even Wisdom must be abandoned, let alone Anti-Wisdom?''

    ~

    \marginpar{\raggedleft VII} ``Subhuti! What is your opinion? Did I gain the `Anuttara-Samyak-Sambodhi'? Did I talk about any `Wisdom'?'' Subhuti answered, ``As far as I comprehended in what you said, there is not a certain `Wisdom', named `Anuttara-Samyak-Sambodhi', and there is also not a certain `Wisdom' that you can talk about. Why? Any Wisdom that you talk about can't be gained, also it can't be talked about: It is not `Wisdom', and it is also not `Anti-Wisdom'. What does it mean? All sages have the Absolute, although what they say may be different.''

    ~

    \marginpar{\raggedleft VIII} ``Subhuti! What is your opinion? If there are some people, who use seven kinds of treasures that can be full of a Gigaworld, to make Alms-Giving, will there be many rewards from merits that they will reap?'' ``There will be a great many, the Respected! Why? The `rewards from merits', are not the essence of `rewards from merits', thus you say that there will be many rewards from merits.'' ``If there are also some people, who accept this scripture, even only four-sentence chant in this scripture, and talk about it to others, there will be more rewards from merits that they will reap than former rewards. Why? Subhuti! All buddhas, and their Anuttara-Samyak-Sambodhi Wisdom, are from this scripture. Subhuti! The Wisdom of buddhas, is not `Wisdom of buddhas'.''

    ~

    \marginpar{\raggedright IX} ``Subhuti! Should any srotapanna believe that `I have achieved Srotapanna'?'' Subhuti answered, ``No, the Respected! Why? `Srotapanna' means `joining the group'. However, there is actually no `joining': Nothing that is able to be seen, heard, smelled, tasted, or touched can be joined, and nothing that is able to exist in consciousness can be joined. Hence there is just a name called `Srotapanna'.'' ``Subhuti! Should any sakadagamin believe that `I have achieved Sakadagamin'?'' Subhuti answered, ``No, the Respected! Why? `Sakadagamin' means `leaving and returning'. However, there is actually no `leaving and returning'. Hence there is just a name called `Sakadagamin'.'' ``Subhuti! Should any anagamin believe that `I have achieved Anagamin'?'' Subhuti answered, ``No, the Respected! Why? `Anagamin' means `no returning'. However, there is actually no `no returning'. Hence there is just a name called `Anagamin'.'' ``Subhuti! Should any arhat believe that `I have achieved Arhat'?'' Subhuti answered, ``No, the Respected! Why? There is actually nothing named `Arhat'. The Respected! If any arhat believe that `I have achieved Arhat', there will be Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. The Respected! You said that I am the best person who has No-Upset-Samadhi (Arana-Samadhi) and I am the first arhat who leaves away from desires. The Respected! I won't believe that `I am an arhat who leaves away from desires'. The Respected! If I believe that `I have achieved Arhat', you won't say that Subhuti is glad of Arana behaviour. Also, there is actually no `Subhuti is glad of Arana behaviour'. Hence there is just a wording that `Subhuti is glad of Arana behaviour'.''

    ~

    \marginpar{\raggedleft X} The Buddha asked Subhuti, ``What is your opinion? Did I gain anything about `Wisdom' in where the Lamp Buddha was?'' ``No! You didn't, the Respected. You didn't gain anything about `Wisdom' in where the Lamp Buddha was.'' ``Subhuti! What is your opinion? Do bodhisattvas `Dignify buddha lands'?'' ``No! They don't, the Respected. Why? The Dignifying buddha lands, is not `Dignifying', and it is just called `Dignifying'.'' ``Therefore, Subhuti! All bodhisattvas, or mahasattvas, need to have clean will in this way: They mustn't be obsessed with anything, which means, they mustn't be obsessed with what are seen, heard, smelled, tasted, touched, and they mustn't be obsessed with consciousness. Subhuti! If a person has a body as huge as the Sumeru Mountain, what is your opinion? Will there be a huge body?'' Subhuti answered, ``It is so huge, the Respected! Why? In your opinion, it is not `body', and it is just called huge `body'.''

    ~

    \marginpar{\raggedright XI} ``Subhuti! What is your opinion? If there are rivers as many as sands in the Ganga River, with sands as many as sands in the Ganga River in each river, will there be many sands in all those rivers?'' ``There will be a great many, the Respected! Even those rivers are countless, let alone the sands?'' ``Subhuti! Now I tell you honestly: If there are some people, who use seven kinds of treasures that can be full of Gigaworlds as many as sands in all those rivers, to make Alms-Giving, will there be many rewards from merits that they will reap?'' Subhuti answered, ``There will be a great many, the Respected!'' ``If there are also some people, who accept this scripture, even only four-sentence chant in this scripture, and talk about it to others, there will be more rewards from merits that they will reap than former rewards.''

    ~

    \marginpar{\raggedright XII} And then the Buddha said, ``Subhuti! If this scripture, even only four-sentence chant in this scripture, is talked about at some places, we should know that all deities, humans, and asuras, should make offerings to these places, as buddha temples and towers, let alone if there are some people, who completely accept this scripture, and read it to others. Subhuti! You should know that they will have comprehended the supreme and rarest Wisdom. Where there is this scripture, there is buddha, and those should be respected as buddha's students.''

    ~

    ~

    \marginpar{\raggedleft XIII} At that time, Subhuti asked the Buddha, ``The Respected! What is the name of this scripture which we should accept?'' The Buddha answered Subhuti, ``The name of this scripture which you should accept, is `Vajra-Prajna-Parami'. What does it mean? Subhuti! The Prajna-Parami, is not `Prajna-Parami', and it is just called `Prajna-Parami'. Subhuti! What is your opinion? Is there any `Wisdom' that I talk about?'' Subhuti answered the Buddha, ``The Respected! There is no `Wisdom' that you `talk about'.'' ``Subhuti! What is your opinion? Are there many tiny dusts in a whole Gigaworld?'' ``There are a great many, the Respected!'' ``Subhuti! The tiny dusts, are not `tiny dusts', and they are just called `tiny dusts'. The Worlds, are not `Worlds', and they are just called `Worlds'. Subhuti! What is your opinion? Can anyone recognize the Like-Arrived by `the thirty two features'?'' ``No, the Respected! No one can recognize the Like-Arrived by `the thirty two features'. Why? The thirty two features, are not `features', and they are just called `the thirty two features'.'' ``Subhuti! If there are some kind people, who use their lives many times, as many as sands in the Ganga River, to make Alms-Giving, and there are also some people, who accept even only four-sentence chant in this scripture, and talk about it to others, there will be a great many rewards from merits that they will reap!''

    ~

    \marginpar{\raggedleft XIV} At that time, Subhuti heard the scripture, and deeply comprehended it. In front of the Buddha, he sobbed, ``Rare, you, the Respected! The scripture you expounded just now is so profound. It is impossible for me to find it, by using Prajna-Eyes I've had so far. The Respected! If there are also some people, who produce the pure belief after knowing this scripture, they will have comprehended the Reality. We should know that they will have reaped the rarest reward. The Respected! The Reality, is not any Phenomenon, thus in your opinion, it is just called `Reality' as a Phenomenon. The Respected! Now I have heard this scripture, and it is not difficult for me to accept, comprehend, and believe in it. Two thousand years later, if there are also some people, who know this scripture, then accept, comprehend, and believe in it, they will be rarest. Why? They won't have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. What does it mean? The Self-Phenomena, are not `Phenomena'. The Otherness-Phenomena, Appearing-Phenomena, Lifetime-Phenomena\dots{}, are also not `Phenomena'. If all `Phenomena' are left away from, there will be buddha.'' The Buddha said to Subhuti, ``Yes! Yes! If there are also some people, who are not in shock, terror, or fear after knowing this scripture, they will be so rare. Why? Subhuti! The first Parami, is not `first Parami', and it is just called `first Parami'. Subhuti! The Insult-Tolerating-Parami, is not `Insult-Tolerating-Parami', and it is just called `Insult-Tolerating-Parami'. Subhuti! For example, when King Kaliraja cut my body, I didn't have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. Why? When I was sliced, if I had Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}, I would have anger and hatred. Subhuti! What's more, I reincarnated five hundred times when I was Insult-Tolerating deity. During that long time, all along, I didn't have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. Subhuti! All bodhisattvas should have Anuttara-Samyak-Sambodhi will, but they must leave away from `Phenomena': They mustn't be obsessed with anything, which means, they mustn't be obsessed with what are seen, heard, smelled, tasted, touched, and they mustn't be obsessed with consciousness. If there is something being obsessed with, it won't be `obsessed' with, thus I say that all bodhisattvas should have the will, and make Alms-Giving without being obsessed with anything. Subhuti! For benefiting all lives, bodhisattvas should make Alms-Giving in this way. The Phenomena, are not `Phenomena'. The lives, are not `lives'. Subhuti! I am truthful, honest, sincere, genuine, veracious. Subhuti! The Wisdom I gain has no certain `Reality', but it is not illusory. Subhuti! If bodhisattvas make Alms-Giving with being obsessed with Wisdom, they will be like being in dark, where they will be able to see nothing. If bodhisattvas make Alms-Giving without being obsessed with Wisdom, they will be like being in light, where they will be able to see everything. Subhuti! Two thousand years later, if there are also some people, who know this scripture, then accept and read it to others, they will have reaped infinite rewards: This is clearly realized by me.''

    ~

    \marginpar{\raggedright XV} ``Subhuti! If there are some kind people, who firstly use their lives many times, as many as sands in the Ganga River, to make Alms-Giving in the morning, then use their lives many times, as many as sands in the Ganga River, to make Alms-Giving at noon, finally use their lives many times, as many as sands in the Ganga River, to make Alms-Giving in the afternoon, also use their lives to make Alms-Giving in this way for countless kalpas, and there are also some people, who produce the eternal belief after knowing this scripture, there will be more rewards from merits that they will reap than former rewards, let alone accept it, and write, read, or expound it to others. Subhuti! Crucially, there are inconceivable, inestimable, infinite rewards in this scripture. I talk for who produce the High-Vehicle, the Highest-Vehicle. If there are some people, who accept this scripture, and read it or widely talk about it to others, they will have reaped inconceivable, inestimable, infinite rewards: This is clearly realized by me. Also they will be shouldering Like-Arrived Anuttara-Samyak-Sambodhi. Why? Subhuti! Who is indulging in low `wisdom', will be being obsessed with Self-View, Otherness-View, Appearing-View, Lifetime-View\dots{}, also they will not be being able to listen and accept it, then read it or expound it to others. Subhuti! All deities, humans, and asuras, should make offerings to anywhere this scripture is. We should know that there are towers, and all of us should respectfully practice services, revolve around, and scatter many kinds of flowers and incenses there.''

    ~

    \marginpar{\raggedleft XVI} And then the Buddha said, ``Subhuti! If there are some kind people, who accept and read this scripture, being despised or defamed by others, it is because they did evil in their former lives, and they would fall into Evil-Path. As they are despised or defamed by others, evil they did in their former lives is annihilated, and they will gain the Anuttara-Samyak-Sambodhi. Subhuti! I remember that I met eight hundred and forty trillion nayuta buddhas before the Lamp Buddha, in the past countless asamkhya kalpas, and I made offerings to all of them without being disrespectful once. If there are also some people, who accept and read this scripture in Doctrine-Decayed-Era, the rewards from merits that they will reap, will be more than one thousand, million, billion, trillion times as many as my rewards from making offerings to all the buddhas, and it is impossible to express how many rewards will they reap by using number. Subhuti! If there are some kind people, who accept and read this scripture in Doctrine-Decayed-Era, there will be so many rewards from merits that they will reap, and if I expound the rewards in detail, some people may become mad and suspicious after hearing what I say. Subhuti! We should know that the content of this scripture is inconceivable, and the effects and rewards from this scripture are also inconceivable.''

    ~

    \marginpar{\raggedright XVII} At that time, Subhuti asked the Buddha, ``The Respected! If kind people spring up the Anuttara-Samyak-Sambodhi will, how can they keep their will, and subdue their unwise minds?'' The Buddha answered Subhuti, ``The kind people, who spring up the Anuttara-Samyak-Sambodhi will, need to keep this will: I should save all lives, however, if I have saved all lives, actually no `lives' will have been saved. Why? Subhuti! If `bodhisattvas' have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}, they can't be bodhisattvas. What does it mean? Subhuti! There is actually no `people who spring up the Anuttara-Samyak-Sambodhi will'. Subhuti! What is your opinion? Was there `The Like-Arrived gained the Anuttara-Samyak-Sambodhi' in where the Lamp Buddha was?'' ``No! there wasn't, the Respected. As far as I comprehended in what you said, there was no `The Like-Arrived gained the Anuttara-Samyak-Sambodhi' in where the Lamp Buddha was.'' The Buddha said, ``Yes! Yes! There was actually no `The Like-Arrived gained the Anuttara-Samyak-Sambodhi'. Subhuti! If there was `The Like-Arrived gained the Anuttara-Samyak-Sambodhi', The Lamp Buddha would not prophesy that `You will be buddha, named Sakya-Muni, in your later life' to me. Since there was actually no `The Like-Arrived gained the Anuttara-Samyak-Sambodhi', The Lamp Buddha prophesied that `You will be buddha, named Sakya-Muni, in your later life' to me. Why? Subhuti! The Like-Arrived, is that any Being (Dharma) is as the content. Subhuti! If someone says that `The Like-Arrived gained the Anuttara-Samyak-Sambodhi', there was actually no `The Like-Arrived gained the Anuttara-Samyak-Sambodhi'. Subhuti! The Anuttara-Samyak-Sambodhi that the Like-Arrived gained has no certain `Reality', but it is not illusory, therefore all Wisdom I talk about, are Wisdom of buddhas. Subhuti! The all Wisdom I talk about, are not `all Wisdom', thus they are just called `all Wisdom'. Subhuti! For example, if a person has a huge body\dots{}'' Subhuti said, ``The Respected! The huge body, is not `huge body', and it is just called `huge body'.'' ``Subhuti! So are bodhisattvas. If a `bodhisattva' says that `I should save infinite lives', the `bodhisattva' should not be called `bodhisattva'. Why? Subhuti! There is actually nothing named `bodhisattva'. Thus I say that nothing is Self, Otherness, Appearing, Lifetime\dots{}. Subhuti! If a `bodhisattva' says that `I should Dignify buddha lands', the `bodhisattva' should not be called `bodhisattva'. Why? The Dignifying buddha lands, is not `Dignifying', and it is just called `Dignifying'. Subhuti! If a `bodhisattva' has achieved No-Self-Wisdom, I will say that the `bodhisattva' is truly named `bodhisattva'.''

    ~

    \marginpar{\raggedleft XVIII} ``Subhuti! What is your opinion? Does Like-Arrived have Flesh-Eyes?'' ``Yes! The Respected, Like-Arrived has Flesh-Eyes.'' ``Subhuti! What is your opinion? Does Like-Arrived have Heaven-Eyes?'' ``Yes! The Respected, Like-Arrived has Heaven-Eyes.'' ``Subhuti! What is your opinion? Does Like-Arrived have Prajna-Eyes?'' ``Yes! The Respected, Like-Arrived has Prajna-Eyes.'' ``Subhuti! What is your opinion? Does Like-Arrived have Dharma-Eyes?'' ``Yes! The Respected, Like-Arrived has Dharma-Eyes.'' ``Subhuti! What is your opinion? Does Like-Arrived have Buddha-Eyes?'' ``Yes! The Respected, Like-Arrived has Buddha-Eyes.'' ``Subhuti! What is your opinion? Did I refer to the sands in the Ganga River?'' ``Yes! The Respected, you referred to the sands.'' ``Subhuti! What is your opinion? If there are rivers as many as sands in the Ganga River, with sands as many as sands in the Ganga River in each river, and there are Worlds as many as sands in all those rivers, will there be many Worlds?'' ``There will be a great many, the Respected!'' The Buddha told Subhuti, ``I clearly know all minds of all lives in those Worlds. Why? The minds, are not `minds', and they are just called `minds'. What does it mean? Subhuti! We can't have minds in the past. We can't have minds at present. We can't have minds in the future.''

    ~

    \marginpar{\raggedright XIX} ``Subhuti! If there are some people, who use seven kinds of treasures that can be full of a Gigaworld, to make Alms-Giving, will there be many rewards from merits that they will reap, because of those causes?'' ``Yes, the Respected! There will be many rewards from merits that they will reap, because of those causes.'' ``Subhuti! If there are really `rewards from merits', I won't say that there are many rewards from merits reaped. Since there are actually no `rewards from merits', I say that there are many rewards from merits reaped.''

    ~

    \marginpar{\raggedleft XX} ``Subhuti! What is your opinion? Can anyone recognize the Like-Arrived by `possession of the body'?'' ``No, the Respected! No one can recognize the Like-Arrived by `possession of the body'. Why? The possession of the body, is not `possession of the body', and it is just called `possession of the body'.'' ``Subhuti! What is your opinion? Can anyone recognize the Like-Arrived by `possession of all the features'?'' ``No, the Respected! No one can recognize the Like-Arrived by `possession of all the features'. Why? The possession of all the features, is not `possession of all the features', and it is just called `possession of all the features'.''

    ~
 
    \marginpar{\raggedleft XXI} ``Subhuti! Don't say that I believe `I talked about some Wisdom'. Don't believe that! Why? If someone says that `The Like-Arrived talked about some Wisdom', I will be defamed, and that is because what I said have not be comprehended. Subhuti! For talking about Wisdom, there is no `Wisdom' to talk about, hence there is just a wording that `talking about Wisdom'.'' At that time, long-lived Subhuti asked the Buddha, ``The Respected! In the future, when the Doctrine-Decayed-Era may come, will any life produce belief after knowing words about this Wisdom?'' The Buddha answered, ``Subhuti! None of them is `life', and none of them is not `life'. Why? Subhuti! The lives, are not `lives', and they are just called `lives'.''

    ~

    \marginpar{\raggedright XXII} Subhuti asked the Buddha, ``The Respected! Is that you gained the Anuttara-Samyak-Sambodhi that you had nothing to be gained?'' The Buddha answered, ``Yes! Yes! Subhuti! For Anuttara-Samyak-Sambodhi, I even don't have anything that is able to be gained, and it is just called `Anuttara-Samyak-Sambodhi'.''

    ~

    \marginpar{\raggedright XXIII} And then the Buddha said, ``Subhuti! For anyone, this Wisdom is equal and never higher or lower, therefore it is named `Anuttara-Samyak-Sambodhi'. Anyone who not only believes in No-Self, No-Otherness, No-Appearing, No-Lifetime\dots{}, but also practices all good behaviours, will have gained the Anuttara-Samyak-Sambodhi. Subhuti! The good behaviours, are not `good behaviours', and they are just called `good behaviours'.''

    ~

    \marginpar{\raggedright XXIV} ``Subhuti! If there are some people, who use seven kinds of treasures that are as large as the whole of all Sumeru Mountains in a Gigaworld, to make Alms-Giving, and there are also some people, who accept this Prajna-Parami scripture, even only four-sentence chant in this Prajna-Parami scripture, and read it or talk about it to others, the rewards from merits that they will reap, will be more than one thousand, million, billion, trillion times as many as former rewards, and it is impossible to express how many rewards will they reap by using number.''

    ~

    \marginpar{\raggedleft XXV} ``Subhuti! What is your opinion? Don't say that I believe `I should save all lives'. Subhuti! Don't believe that! Why? There is actually no `life' that I save. If there is `life' that I save, I will have Self-Concept, Otherness-Concept, Appearing-Concept, Lifetime-Concept\dots{}. Subhuti! The Self-Concept\dots{}, is not `Self-Concept'\dots{}, but the mediocre have Self-Concept\dots{}. Subhuti! The mediocre, are not `the mediocre', and they are just called `the mediocre'.''

    ~

    \marginpar{\raggedleft XXVI} ``Subhuti! What is your opinion? Can anyone recognize the Like-Arrived by `the thirty two features'?'' Subhuti answered, ``Yes! Yes! Recognize the Like-Arrived by `the thirty two features'.'' The Buddha replied, ``Subhuti! If recognizing the Like-Arrived by `the thirty two features', the noble kings will be the same as the Like-Arrived.'' Subhuti replied the Buddha, ``The Respected! As far as I comprehended in what you said, no one should recognize the Like-Arrived by `the thirty two features'.'' At that time, the Buddha taught a chant: If people recognize me, by `what are seen or heard', they will take the wrong path, which means they can't recognize the Like-Arrived.

    ~

    \marginpar{\raggedleft XXVII} ``Subhuti! If you believe that I gain the `Anuttara-Samyak-Sambodhi' because I don't believe possession of the features, don't believe that I gain the `Anuttara-Samyak-Sambodhi' because I don't believe possession of the features. Subhuti! If you believe that who has the Anuttara-Samyak-Sambodhi will will say that all Being will Annihilate, don't believe that! Why? Who has the Anuttara-Samyak-Sambodhi will will not say that all Being will Annihilate.''

    ~

    \marginpar{\raggedright XXVIII} ``Subhuti! If there are some bodhisattvas, who use seven kinds of treasures that can be full of Worlds as many as sands in the Ganga River, to make Alms-Giving, and there are also some people, who know that all Being are without Self, and succeed in Tolerating, there will be more rewards from merits that these bodhisattvas will reap than former ones. Why? Subhuti! That is because none of bodhisattvas accepts the rewards.'' Subhuti asked the Buddha, ``The Respected! Why you say that none of bodhisattvas accepts the rewards?'' ``Subhuti! They mustn't be obsessed with the rewards, therefore I say that none of bodhisattvas accepts the rewards.''

    ~

    \marginpar{\raggedright XXIX} ``Subhuti! If someone says that `The Like-Arrived comes and goes, sits and lies', what I said will not have been comprehended. Why? The Like-Arrived, never arrives from or to somewhere, therefore the name is `Like-Arrived'.''

    ~

    \marginpar{\raggedright XXX} ``Subhuti! What is your opinion? If kind people, even Gigaworlds are separated into tiny dusts, will there be many tiny dusts?'' Subhuti answered, ``There will be a great many, the Respected! Why? If there are really `tiny dusts', you won't say that they are tiny dusts. What does it mean? The tiny dusts, are not `tiny dusts', and they are just called `tiny dusts'. The Respected! The Gigaworlds, are not `Worlds', and they are just called `Worlds'. Why? If there are really `Worlds', they will be Entireties. The Entireties, are not `Entireties', and they are just called `Entireties'.'' ``Subhuti! The Entireties can't be talked about, but the mediocre are obsessed with them.''

    ~

    \marginpar{\raggedleft XXXI} ``Subhuti! If someone says that `The Buddha talks about Self-View, Otherness-View, Appearing-View, Lifetime-View\dots{}', will what I said have been comprehended?'' ``No, the Respected! What you said will not have been comprehended. Why? The Self-View, Otherness-View, Appearing-View, Lifetime-View\dots{}, are not `Self-View', `Otherness-View', `Appearing-View', `Lifetime-View'\dots{}, and they are just called `Self-View', `Otherness-View', `Appearing-View', `Lifetime-View'\dots{}.'' ``Subhuti! For any Being, who spring up the Anuttara-Samyak-Sambodhi will, must know the view like this, then comprehend and believe in it, and they mustn't have Wisdom-Concept. Subhuti! The Wisdom-Concept, is not `Wisdom-Concept', and it is just called `Wisdom-Concept'.''

    ~

    \marginpar{\raggedleft XXXII} ``Subhuti! If there are some people, who use seven kinds of treasures that can be full of countless asamkhya Worlds, to make Alms-Giving, and there are also some kind people, who spring up the Bodhi will, accept this scripture, even only four-sentence chant in this scripture, and read it or talk about it to others, there will be more rewards from merits that they will reap than former rewards. Why talk about it to others? Never being obsessed with Phenomena, there will be the invariable Reality. Why? All the Relative, are like dreams, illusions, bubbles, shadows, dew drops and lightning flashes: This is what we must believe in.'' The Buddha had completed preaching. Not only elder Subhuti, but all bhiksus, bhiksunis, upasakas, upasikas, deities, humans, and asuras, are full of joy after hearing what the Buddha said, and they all accept and believe in it.

\end{document}
